Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-03 Article.tex

\textcolor{red}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallographic analysis difficult.
Hence simpler techniques, like developing analytical models have been implemented.
Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.

>>>>

\textcolor{red}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
Hence simpler techniques, like developing analytical models have been implemented.
Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.
